Turbo fast no compromise gravitational wave parameter estimation

### 2022-11-02 src/tex/ms.tex
Add abstract

% Abstract with filler text
\begin{abstract}
We do one thing and one thing only, gravitational wave parameters estimation, and we do it in turbo mode.
\end{abstract}

>>>>

% Abstract with filler text
\begin{abstract}
We present a light-weighted, flexible and high performance framework to estimate
gravitational wave event parameters. By combining heterodyned likelihood,
automatically differentiable and accelerators compatible waveforms, normali zing
flow enhanced gradient-based MCMC, we achieve parameter estimation for real
event like GW150914 and GW170817 within a minute of sampling time with little to
no compromise. Our framework does not require pre-training or explicit
reparameterization, and can be generalized to handle higher dimensional
problems. We also discuss as near-real time parameter estimation have been shown
to be possible by multiple groups, what are the trade-offs and future
developments the community should be aware of. Our code for generating the
manuscript and running the analysis is publically available on github.
\end{abstract}
